Abstractions for Multi-Sorted Substitutions

### 2023-07-11 paper/paper.tex
Update.

  \subsection{Multi-Sorted Syntax}
  % Instead we define a single term type which is indexed by the sort of
  % syntax, i.e.\ whether the term is a kind, type, or expression:
  To avoid these drawbacks, we define a single term type \texttt{S~⊢~s} that is indexed by its sort \texttt{s},
  i.e.\ whether the term is a kind, type, or expression, and the sorts of its free variables \texttt{S}:

  For example a term of type \texttt{[𝕥, 𝕥] ⊢ 𝕖} is an expression (\texttt{𝕖}) with two free type-variables (\texttt{𝕥}).
  \LibCode\KSortTy

  \AppCode\FSort

  \LibCode\KVariables
  \AppCode\FSyntax
  The variable constructor \texttt{'\_} takes a sorted DeBruijn-index \texttt{S~∋~s}.
  Since the \texttt{Sort}s in \texttt{S} are restricted to the sort-type \texttt{Var}, it is not possible to construct kind-variables.

  \subsection{A Structure for Multi-Sorted Syntax}
  \LibCode\KTerms
  \AppCode\FTerms

>>>>

  \subsection{Multi-Sorted Syntax}
  To avoid these drawbacks, we define the whole syntax as a single sort-indexed type of terms.

  A sort describes to which syntactic category a term belongs and is
  itself indexed by a sort type which describes whether the syntax
  permits variables of this sort:
  \LibCode\KSortTy
  \AppCode\FSort

  The term type \texttt{S~⊢~s} is then indexed by its sort \texttt{s} and the sorts of its free variables \texttt{S}.
  For example, \texttt{[𝕥, 𝕥] ⊢ 𝕖} is the type of expressions (\texttt{𝕖}) with two free type-variables (\texttt{𝕥}).
  \newpage
  \AppCode\FSyntax
  The notation \texttt{\_⊢\_} is often used for well-typed terms in
  intrinsically-typed languages. This is no accident: in effect, we
  defined an intrinsically-typed language with the twist that the
  typing relation assures exactly that the syntactic categories are followed.
  Sorts \texttt{s} correspond to types, and lists of sorts \texttt{S}
  correspond to type environments.

  As it is typical in intrinsic typing, variables are represented as
  typed (in our case sorted) DeBruijn indices \texttt{S~∋~s}, i.e.\
  values of the usual proof-relevant list-membership relation:
  \LibCode\KVariables

  Contrary to the usual intrinsic typing, we limit the environment
  \texttt{S} to sorts with index \texttt{Var}.
  This ensures that it is impossible to construct kind variables, as
  it is not possible to extend \texttt{S} with the sort of kinds
  \texttt{𝕜}.

  \subsection{A Structure for Multi-Sorted Syntax}
  The rest of our formalization builds on top of a multi-sorted
  syntax, which we capture in the following structure:
  \LibCode\KTerms
  Aside from capturing our syntactic definitions, we require a proof that the
  variable introduction \texttt{`\_} is injective. This is trivially true
  for all constructors. The instantiation for our System F syntax is straightforward:
  \AppCode\FTerms
